A large-scale analysis of racial disparities in police stops across the

### 2019-07-29 lib/paper_results.Rmd
progress

---
title: "A large-scale analysis of racial disparities in police stops across the
United States"
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
source(here::here("lib", "utils.R"))
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(tinytex.verbose = TRUE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

\begin{center}
\section{Basic Numbers}
\end{center}

@@

\begin{center}
\section{Prima Facie Stats}
\end{center}

```{r stop_rates}
pfs$plots$stop
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

@@

```{r search_rates}
pfs$plots$search
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

\newpage
\begin{center}
\section{Veil of Darkness}
\end{center}

```{r veil_of_darkness-plot-630, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`6:30pm`
```
```{r veil_of_darkness-plot-645, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`6:45pm`
```
```{r veil_of_darkness-plot-700, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`7:00pm`
```
```{r veil_of_darkness-plot-715, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`7:15pm`
```
```{r veil_of_darkness-plot-730, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`7:30pm`
```
```{r veil_of_darkness-plot-745, fig.height = 3, fig.width = 4}
vod$full$plots$states$TX$`7:45pm`
```

\subsection(Main model results)

@@

\subsection(Model results for the appendix/footnote reference)

@@

\begin{center}
\section{Search Disparity Analysis}
\end{center}

@@

\begin{center}
\subsection{Outcome test results}
\end{center}

```{r disparity-city-hit_rates-table}
kable(disp$city$outcome$results$aggregate_hit_rates)
```
```{r disparity-state-hit_rates-table}
kable(disp$state$outcome$results$aggregate_hit_rates)
```
\newpage
```{r disparity-city-hit_rates-plot, fig.height = 2, fig.width = 4}
disp$city$outcome$plots$aggregate +
  theme(legend.position = "none")
```
```{r disparity-state-hit_rates-plot, fig.height = 2, fig.width = 2}
disp$state$outcome$plots$aggregate +
  theme(legend.position = "none")
```

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 6}
disp$city$threshold$plots$aggregate 
  # theme(legend.position = "none")
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 6}
disp$state$threshold$plots$aggregate 
  # theme(legend.position = "none")
```
\newpage
```{r disparity-city-ppc-search, fig.height = 5, fig.width = 8}
disp$city$threshold$ppc$search_rate
```
```{r disparity-city-ppc-hit, fig.height = 5, fig.width = 8}
disp$city$threshold$ppc$hit_rate
```

\newpage
```{r disparity-state-ppc-search, fig.height = 5, fig.width = 8}
disp$state$threshold$ppc$search_rate
```
```{r disparity-state-ppc-hit, fig.height = 5, fig.width = 8}
disp$state$threshold$ppc$hit_rate
```

@@

\begin{center}
\section{Marijuana Legalization Analysis}
\end{center}
```{r mj_table}
kable(mj$tables$search_rate_difference_in_difference_coefficients)
```

\newpage
```{r mj_test_search_rates_plot, fig.height = 3, fig.width = 7}
mj$plots$test_search_rates 
# theme(
#     legend.position = c(0.88, 0.80),
#     axis.title.y = element_text(size = 12)
#   )
```

```{r mj_test_misdemeanor_rates_plot, fig.height = 3, fig.width = 7}
mj$plots$test_misdemeanor_rates 
  # theme(
  #   legend.position = c(0.88, 0.80),
  #   axis.title.y = element_text(size = 12)
  # )
```

```{r mj_inferred_threshold_plot, fig.height = 3, fig.width = 7}
mj$plots$inferred_threshold_changes
```

```{r save_mj_control_search_rates, eval=FALSE}
# NOTE: have to save the file to the tmp directory because landscape doesn't
# work with r execution blocks
library(ggplot2)
ggsave(
  "/tmp/mj_control_search_rates.png",
  mj$plots$control_search_rates,
  height = 6,
  width = 11
)
```

>>>>

---
title: "A large-scale analysis of racial disparities in police stops across the
United States"
classoption: landscape
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

\section{Basic Numbers}

@@

\section{Prima Facie Stats}

```{r stop_rates}
pfs$rates$stop %>%
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_annual_stop_rate = mean(annual_stop_rate)) %>%
  kable()
```

@@

```{r search_rates}
pfs$rates$search %>% 
  mutate(agency = if_else(city == "Statewide", "state patrol", "municipal pd")) %>% 
  group_by(agency, subject_race) %>%
  summarize(average_search_rate = mean(search_rate)) %>%
  kable()
```

\section{Veil of Darkness}

```{r veil_of_darkness-plot-630, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`6:30pm`
```

```{r veil_of_darkness-plot-645, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`6:45pm`
```

```{r veil_of_darkness-plot-700, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:00pm`
```

```{r veil_of_darkness-plot-715, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:15pm`
```

```{r veil_of_darkness-plot-730, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:30pm`
```

```{r veil_of_darkness-plot-745, fig.height=6, fig.width=9}
vod$full$plots$states$TX$`7:45pm`
```

\subsection{Main model results}

@@

\newpage
\subsection{Model results for the appendix/footnote reference}

@@

\section{Search Disparity Analysis}

@@

\subsection{Outcome Test}

```{r disparity-hit_rates-tables}
kable(disp$city$outcome$results$aggregate_hit_rates)
kable(disp$state$outcome$results$aggregate_hit_rates)
```

@@

```{r disparity-city-hit_rates-plot, fig.height=6, fig.width=10}
disp$city$outcome$plots$aggregate + theme(legend.position = "none")
```

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
disp$state$outcome$plots$aggregate + theme(legend.position = "none")
```

\subsection{Threshold test results}

```{r disparity-thresholds-tables}
kable(disp$city$threshold$results$aggregate_thresholds)
kable(disp$state$threshold$results$aggregate_thresholds)
```

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
disp$city$threshold$plots$aggregate + theme(legend.position = "none")
```

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$plots$aggregate + theme(legend.position = "none")
```

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$ppc$search_rate
```

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$ppc$hit_rate
```

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$ppc$search_rate
```

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$ppc$hit_rate
```

\section{Marijuana Legalization Analysis}

```{r mj_table}
kable(mj$tables$search_rate_difference_in_difference_coefficients)
```

```{r mj_treatment_search_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_search_rates + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```

```{r mj_treatment_misdemeanor_rates_plot, fig.height=5, fig.width=10}
mj$plots$treatment_misdemeanor_rates + theme(
  legend.position = c(0.88, 0.80),
  axis.title.y = element_text(size = 12)
)
```

```{r mj_inferred_threshold_plot, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes
```

```{r save_mj_control_search_rates, fig.height=5, fig.width=10}
mj$plots$control_search_rates
```
